\chapter{Introduction}

In the first version of this book,
\textbf{The Definitive Guide to Apache mod\_rewrite}\\
(http://drbacchus.com/book/rewrite),
which was published in 2006, I only talked about mod\_rewrite. But,
with the release of Apache httpd 2.4 in February of 2012, the
world of complex URL mapping is so much bigger than that. In addition to mod\_rewrite`, a number of
new standard modules have joined the game, as well as a number of
powerful core features, which make mod\_rewrite just one of many tools
in your bag of tricks.

And so the scope of this book has expanded to include not merely URL
rewriting, but also methods for munging (modifying) content, and
dynamic conditional configuration. In many cases, these techniques make
mod\_rewrite unnecessary, or, at least, provide easier alternatives, so
they fit the scope of the book very well.

These techniques include mod\_substitute, mod\_proxy\_html, the Define
directive, the <If> container, mod\_macro, and many more. Along the
way, we'll also discuss the various parts of URL mapping, the
understanding of which allows you to avoid using these more complicated
techniques.

While all of these are covered in the formal documentation\\
(http://httpd.apache.org/docs/current), this book offers a companion
to hold your hand and offer you more in depth assistance in your journey
towards Apache httpd mastery.

\section{About this book}

This book was written using TexStudio, vim, and various Perl scripts, and is written in \LaTeX. It is available in a
variety of formats, and you can always obtain the most recent version of
the book at \verb~http://rewrite.rcbowen.com/~, and you'll usually be able to buy a fairly recent version
in the Amazon Kindle store. Some day, there will hopefully be a printed version, too.

You may check out the bleeding edge version of this book from svn at \verb~http://svn.rcbowen.com/svn/public/mod_rewrite_book/~ and are encouraged to submit patches against HEAD. If you don't know what that means, you are welcome to submit errata to \verb~rbowen@rcbowen.com~, and some day there will be a handy way to do this on the website. Not today.

This book is a work in progress. If you purchased the book in electronic
form, you should be eligible to receive updates from wherever you bought
it. If you're not, send me your email receipt (rbowen@rcbowen.com), 
and I'll send you an updated version.

A brief word about the documentation. The official docs, at \verb~http://httpd.apache.org/docs/~, are great, and are the work of many dedicated people. I'm one of many. This book is intended to augment those docs, and not replace them. If it appears sometimes that I have copied shamelessly from the documentation, I humbly ask you to remember that I participated in writing those docs, and the edits flowed both directions.

\section{About the author}

Rich Bowen has been involved on the Apache http server documentation
since about 1998. He is also the author of \textbf{Apache Cookbook}, and \textbf{The
Definitive Guide to Apache mod\_rewrite}. You can frequently find him in
\#httpd, on irc.freenode.net. under the name of DrBacchus.

Rich is the Community Manager at SourceForge, where he tries to help a few
hundred thousand Open Source projects in whatever ways they need.

He lives in Lexington, Kentucky, with his wife and kids. If you want a cat, drop by.

\section{Acknowledgements}

Many thanks to TeXstudio (\verb~http://texstudio.sourceforge.net/~) for an amazing product. Although I've been writing \LaTeX  for years in vim, TeXstudio took a lot of the guesswork out of the process this time around.

Thanks to \verb~fajita~, and the other regulars on \#httpd (on the irc.freenode.net network). \verb~fajita~ is my research assistant, and knows more than everyone else on the channel put together. And the folks on \#ahd keep me sane. Or insane. Depending on how you measure. A warm hog to each of you.

